% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

  
 \moveleft.5\hoffset\centerline{\large\bf SONIA SOUBAM}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\address{Email: sonias@iiitd.ac.in\\Web: soubam.github.io}
\address{B307 MUC PhD Lab\\Academic Block\\IIIT Delhi\\Okhla Phase-3\\ New Delhi-110020 }
                                  
\begin{resume}

%\section{About Myself}
%I am technology enthusiasts with a keen interest on using developing technologies in making day-to-day life simpler and convenient. I am looking for an opportunity to be associated with organisation which is dedicated in using technology for comfortable way of living.
 
\section{EDUCATION}          
\begin{itemize}
\item PhD Scholar IIIT Delhi, Mobile and Ubiquitous Computing (Since July, 2013 to present)
\item MTech Computer Science with Specialization Information Security, IIIT Delhi, May 2013.
\item BE Computer Science and Engineering, Anna University, Coimbatore, May 2011.
\item XIIth, Herbert School, Imphal, Manipur, 2007.
\item Xth, Little Flower School, Imphal, Manipur, 2005.
\end{itemize}
 

\section{RESEARCH INTERESTS}        
\begin{itemize}
  \item Human activity detection using smartphone and wearable sensors
  \item Participatory sensing using mobile phone sensors
\end{itemize}  
        
 
 
\section{PUBLICATIONS}          
   \begin{itemize}
   \item S. Soubam, M. Agarawal, V. Naik. Using an Arduino and a Smartwatch to Measure Liquid Consumed From Any Container. (WACI 2017 co-located with IEEE Comsnets 2016)
   \item \textbf{S. Soubam}, N. Goyal, N. Adhikari, V. Naik . Understanding the Routine Activities of Students in Campus using Smartphone Sensors. Proceedings of the 14th Annual International Conference on Mobile Systems, Applications, and Services Companion, June 26-30, 2016, Singapore [Poster]
   \item \textbf{S. Soubam}, D. Banerjee, V. Naik, and D. Chakraborty.  \textit{BluePark: Tracking Parking and Un-parking Events in Indoor Parking Lots}, Accepted at International Conference on Distributed Computing and Networking (ICDCN 2016), Jan 4-7, 2016, Singapore.
   \item \textbf{S. Soubam}, \textit{Detection of Day-to-Day Complex Human Activities using Smartphones}, [PhD Forum, COMSNET 2015]
   \item \textbf{S. Soubam}, V. Naik, and D. Chakraborty. \textit{Detection of Day-to-Day Human Activities using Smart phones.} Accepted at 1st Xerox Research Centre India (XRCI) Open, Mar 14, 2014, Bangalore, India [Poster]

   \item K. Yadav, D. Chakraborty, \textbf{S. Soubam}, N. Prathapaneni, V. Nandakumar, N. Rajamani, L. V. Subramaniam, S. Mehta, and P. De. \textit{Human Sensors: Case-study of Open-ended Community Sensing in Developing Regions}. Accepted at the The IEEE Pervasive Computing and Communication (PerCom) Conference Work in Progress, March 18-22, 2013, San Diego, USA
   
   \item \textbf{S. Soubam}, N. Prathapaneni, V. Nandakumar, K. Yadav, N. Rajamani, D. Chakraborty, L. V. Subramaniam, S. Mehta, and P. De. \textit{Open-Ended Community-Sensing: Data Collection and Processing.} Accepted at the Sixth Workshop on Analytics for Noisy Unstructured Text Data (AND'12), IIT Bombay, Mumbai, India
   \end{itemize}        

\section{PATENTS}
\begin{itemize}
\item \textit{Automatic indoor parking system using collaborative smartphone sensing}
\begin{itemize}
\item[-] \textbf{Inventors:}  Dipyaman Banerjee, Sonia Soubam
\item[-] Filed for US Patent in August 2015
\item[-] Based on work done during IBM Research Summer Internship 2014
\end{itemize}

\item \textit{Handwritten homework monitoring using wearable device}
\begin{itemize}
\item[-] \textbf{Inventors:}  Ruhi Sharma, Vijay E, Nitendra Rajput, Prasenjit Dey, Dipyaman Banerjee, Sonia Soubam
\item[-] Filed for US Patent in November 2016
\item[-] Based on work done during IBM Research Summer Internship 2016
\end{itemize}
\end{itemize}

 \section{MTECH THESIS}
                    
                     \begin{itemize}  \itemsep -2pt %reduce space between items
                     \item \textbf{Location Privacy in MobiShare}
                     \begin{itemize}
                     \item[-] Designed a Privacy Preserving protocol for exchanging and comparing proximity of users in a location based file exchange service.
                     \end{itemize}
                    \end{itemize}



   
    
 \section{Internship/Teaching Assistantship}
 \begin{itemize}
 \item Research Intern, IBM India Research Labs, New Delhi, India (June - August, 2016)
\item Research Intern, IBM India Research Labs, New Delhi, India (May - July, 2014)
 \item Teaching Assistant, Mobile Computing (Monsoon Semester, 2013) Instructor: Dr. Vinayak Naik
 \end{itemize}
   

 
 \section{PROJECTS}
   \begin{itemize}
  \item Implemented Auto-completion feature for Galago Search Engine
   \item Android Application : Phone as a Wireless Microphone
      \item Digital Forensics: Changing MAC DTS of call and SMS in Android

      \item Platform for Privacy Preferences Project (P3P ) implementation of Website
   \end{itemize}  
 
  \section{COMPUTER SKILLS}
 \begin{itemize}
 \item \textbf{Languages: } Java, Python, Matlab, R, MySQL
 \item \textbf{Others: } Android, Django, WEKA  
 \end{itemize}
 
 \section{ACHIEVEMENTS}
 \begin{itemize}
 \item Third prize at the Innovation Challenge in Research Showcase'17, IIIT-Delhi.
 \item Best paper award for paper at Workshop on Wild and Crazy Ideas on the interplay between IoT and Big Data (WACI'17) in conjunction with the 9th International Conference 
  \item Best Poster Award in IBM Summer Internship, 2016.
  \item Awarded IBM Ph.D. fellowship for the year 2016-2018

 \item Secured 24th State Rank on High School Leaving Certificate Examination, 2005.
 \end{itemize}
 
 \section{OTHERS}
 \begin{itemize}
 \item Volunteer at Workshop on Ubiquitous Sensing for Effective Living held at IIIT-D.
  \item Received full travel grant from UNESCO to attend Workshop on Scientific Applications for the Internet of Things (IoT) at the Abdus Salam International Centre for Theoretical Physics (ICTP) of UNESCO, Trieste, Italy
 \item Attended Big Data \& Analytics School, IBM-iCARE 2013, New Delhi, India.
 \end{itemize}
 

 
  \section{EXTRACURRICULAR ACTIVITIES}
 \begin{itemize}
  \item Represented Anna University Coimabatore at Inter-University Table Tennis Tournament. 
  \item Won first price in Technical Quiz Competition in XRCI, 2014.
 \end{itemize}

  \section{REFERENCES}
 \begin{itemize}
  \item Vinayak Naik, Associate Professor, IIIT-Delhi, naik@iiitd.ac.in
  \item Dipanjan Chakraborty, Director, Mosix Technologies, dipanjan.chakraborty@gmail.com 
 % \item Dipyaman Banerjee, IBM Research India, Delhi, dipyaban@in.ibm.com
  %\item Nitendra Rajput, IBM Research India, Delhi, rnitendra@in.ibm.com 
   \end{itemize} 

\end{resume}
\end{document}